BIP Architectures and Open pNets

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
arch-pNets: (Minor) INRIA --> Inria
arch-pNets: Minor edits

\institute{%
  INRIA Lille -- Nord Europe, Villeneuve d'Ascq, France\\
  \email{simon.bliudze@inria.fr}
  \and
	Univ Lyon, CNRS, ENS de Lyon, Inria, Universit\'e Claude Bernard Lyon 1, LIP UMR 5668, Lyon, France\\\email{ludovic.henrio@ens-lyon.fr}
  \and
    Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia-Antipolis, France\\
  \email{eric.madelaine@inria.fr}
}

@@

The concepts and results of the paper are illustrated by a running
example extending the Failure Monitor architecture from the CubETH
nanosatellite on-board software case-study~\cite{CubETH-case-study}.

@@

@@

@@

\subsection{Full results of the use-case}
\label{secn:full-results}

>>>>

\institute{%
  Inria Lille -- Nord Europe, Villeneuve d'Ascq, France\\
  \email{simon.bliudze@inria.fr}
  \and
	Univ Lyon, CNRS, ENS de Lyon, Inria, Universit\'e Claude Bernard Lyon 1, LIP UMR 5668, Lyon, France\\\email{ludovic.henrio@ens-lyon.fr}
  \and
    Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia-Antipolis, France\\
  \email{eric.madelaine@inria.fr}
}

@@

The concepts and results of the paper are illustrated by a running
example extending the Failure Monitor architecture from the CubETH
nanosatellite on-board software case study~\cite{CubETH-case-study}.

@@

\subsection{Verification of the characteristic properties}
\label{secn:arch:verif}

@@

\subsection{Composition of architectures}
\label{secn:arch:composition}

@@

\subsection{Full results of the case study}
\label{secn:full-results}
